Figure 1 doublets

### 2020-02-03 main_figures/doublets.Rmd
replace load_all with normal lib

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ROCit)
  library(ggplot2)
  library(cowplot)
})
devtools::load_all("~/bioinfo/robinson/scDblFinder/")
theme_set(theme_cowplot(font_size = 12))

>>>>

```{r}
suppressPackageStartupMessages({
  library(SingleCellExperiment)
  library(ROCit)
  library(ggplot2)
  library(cowplot)
  library(scDblFinder)
})
theme_set(theme_cowplot(font_size = 12))
